---
title: "Multilevel models for desegregation paper"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_depth: 4
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = T, warning = FALSE, message = FALSE, out.width="100%")
```

```{r message=FALSE, warning=FALSE, echo=FALSE}
# Libraries
pacman::p_load(tidyverse, haven, lme4, stargazer, texreg, AER, performance, knitr)

# Parameters
data_file <- here::here("data/stu_admin_all_with_netvars.Rds")
trends_file <- here::here("data/trends.csv")
newscores_file <- here::here("data/new_scoring/friends/newscores.Rds")
fac_res_file <- here::here("data/fac_res_prop.csv")
```


```{r, message=F, warning=F, echo=F}
df <-
  data_file %>%
  read_rds() %>% 
  #filter(stu_merge == 3) %>% 
  mutate_at(vars(contains("ea_seats_reser")), replace_na, replace = 0) %>% 
  left_join(read_rds(newscores_file), by = "stdid") %>% 
  left_join(read_csv(fac_res_file), by = "department_id") %>% 
  mutate(
    female = gender - 1,
    age = 2017 - lubridate::year(b_birthdate),
    reservation = dplyr::recode(reservation, "Non-reservation" = 0L, "Reservation" = 1L, .default = NA_integer_),
    stu_res_official = (ea_seats_reserved_students_obc + ea_seats_reserved_students_sc + ea_seats_reserved_students_st) / 100,
    fac_res_official = (ea_seats_reserved_faculty_obc + ea_seats_reserved_faculty_sc + ea_seats_reserved_faculty_st) / 100,
    z_seg_g1 = if_else(grade == 2, b_seg_new, NA_real_),
    z_seg_g2 = if_else(grade == 2, e_seg_new, NA_real_),
    z_seg_g3 = if_else(grade == 4, b_seg_new, NA_real_),
    z_seg_g4 = if_else(grade == 4, e_seg_new, NA_real_)
  ) 

baseline_achievement <-
  df %>%
  select(
    classid,
    stdid,
    b_math_g1_score,
    b_math_g3_score,
    b_physics_g1_score,
    b_physics_g3_score,
    b_ct_score,
    b_ql_score,
    b_rr_score
  ) %>%
  group_by(classid) %>%
  mutate_at(vars(ends_with("score")), ~ scale(.) %>% pnorm()) %>%
  ungroup() %>%
  transmute(stdid,
            b_score =
              pmap_dbl(select(., ends_with("score")),
                       ~ mean(c(...), na.rm = TRUE)))

df <-
  df %>%
  left_join(df %>%
              group_by(department_id) %>%
              summarize(stu_res_actual = mean(reservation, na.rm = TRUE)),
            by = "department_id") %>%
  mutate_at(vars(starts_with(c(
    "stu_res_", "fac_res_", "z_seg_g"
  )), b_seg_new, e_seg_new, age),
  ~ scale(.) %>% as.vector) %>%
  left_join(baseline_achievement, by = "stdid") %>%
  rename(
    diverse_dorms = ea_polic_integration_students4,
    mentoring_programs = ea_polic_integration_students3,
    integration_courses = ea_polic_integration_students6,
    diversity_office = ea_staff_strength_scsctcell
  ) %>%
  mutate(
    diversity_office = if_else(
      diversity_office > 0 &
        !is.na(diversity_office),
      1,
      diversity_office
    ) %>% as.integer()
  )
```


## Levels

*Department (Level 2) &#8594; Student (Level 1)*

(`department_id` &#8594; `student`)

<br/>
Glimpse of how the data is structured:

```{r, echo=F}
df %>%
  arrange(-stu_merge, department_id, stdid) %>%
  select(department_id, stdid, grade, reservation, contains(c("z_seg_g1", "z_seg_g2")))
```


## Null model

### Model summary

```{r, results="asis"}
lm1.1 <-
  lmer(z_seg_g2 ~ 1 + (1 |
                         department_id),
       data = df %>% filter(reservation == 1))
lm1.2 <-
  lmer(z_seg_g2 ~ 1 + (1 |
                         department_id),
       data = df %>% filter(reservation == 0))
lm1.3 <-
  lmer(z_seg_g4 ~ 1 + (1 |
                         department_id),
       data = df %>% filter(reservation == 1))
lm1.4 <-
  lmer(z_seg_g4 ~ 1 + (1 |
                         department_id),
       data = df %>% filter(reservation == 0))

knitreg(
  list(lm1.1, lm1.2, lm1.3, lm1.4),
  custom.note = "%stars",
  stars = c(0.01, 0.05, 0.1),
  include.ci = FALSE,
  include.variance = TRUE,
  custom.model.names = c(
    "Cohort 1 Res",
    "Cohort 1 Non-res",
    "Cohort 2 Res",
    "Cohort 2 Non-res"
  )
)
```


### Model ICC

```{r}
bind_rows(
  icc(lm1.1, by_group = T),
  icc(lm1.2, by_group = T),
  icc(lm1.3, by_group = T),
  icc(lm1.4, by_group = T),
  .id = "model"
) %>%
  pivot_wider(names_from = model, values_from = ICC) %>%
  select(
    level = Group,
    "Cohort 1 Res" = "1",
    "Cohort 1 Non-res" = "2",
    "Cohort 2 Res" = "3",
    "Cohort 2 Non-res" =  "4"
  ) %>%
  kable()
```


## Adding student level predictors

### Model summary

```{r, results="asis"}
lm2.1 <-
  lmer(
    z_seg_g2 ~ z_seg_g1 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + (1 |
                                                                                                                                                 department_id),
    data = df %>% filter(reservation == 1)
  )

lm2.2 <-
  lmer(
    z_seg_g2 ~ z_seg_g1 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + (1 |
                                                                                                                                                 department_id),
    data = df %>% filter(reservation == 0)
  )

lm2.3 <-
  lmer(
    z_seg_g4 ~ z_seg_g3 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + (1 |
                                                                                                                                                 department_id),
    data = df %>% filter(reservation == 1)
  )

lm2.4 <-
  lmer(
    z_seg_g4 ~ z_seg_g3 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + (1 |
                                                                                                                                                 department_id),
    data = df %>% filter(reservation == 0)
  )

knitreg(
  list(lm2.1, lm2.2, lm2.3, lm2.4),
  custom.note = "%stars",
  stars = c(0.01, 0.05, 0.1),
  include.ci = FALSE,
  include.variance = TRUE,
  custom.model.names = c(
    "Cohort 1 Res",
    "Cohort 1 Non-res",
    "Cohort 2 Res",
    "Cohort 2 Non-res"
  )
)
```


### Model ICC

```{r}
bind_rows(
  icc(lm2.1, by_group = T),
  icc(lm2.2, by_group = T),
  icc(lm2.3, by_group = T),
  icc(lm2.4, by_group = T),
  .id = "model"
) %>%
  pivot_wider(names_from = model, values_from = ICC) %>%
  select(
    level = Group,
    "Cohort 1 Res" = "1",
    "Cohort 1 Non-res" = "2",
    "Cohort 2 Res" = "3",
    "Cohort 2 Non-res" =  "4"
  ) %>%
  kable()
```


## Adding department level predictors

Student level predictors are still included (even though not shown in results below)

### Model summary

```{r, results="asis"}
lm3.1 <-
  lmer(
    z_seg_g2 ~ z_seg_g1 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + stu_res_official + fac_res_official + diverse_dorms + mentoring_programs + integration_courses + diversity_office + (1 |
                                                                                                                                                                                                                                                                     department_id),
    data = df %>% filter(reservation == 1)
  )

lm3.2 <-
  lmer(
    z_seg_g2 ~ z_seg_g1 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + stu_res_official + fac_res_official + diverse_dorms + mentoring_programs + integration_courses + diversity_office + (1 |
                                                                                                                                                                                                                                                                     department_id),
    data = df %>% filter(reservation == 0)
  )

lm3.3 <-
  lmer(
    z_seg_g4 ~ z_seg_g3 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + stu_res_official + fac_res_official + diverse_dorms + mentoring_programs + integration_courses + diversity_office + (1 |
                                                                                                                                                                                                                                                                     department_id),
    data = df %>% filter(reservation == 1)
  )

lm3.4 <-
  lmer(
    z_seg_g4 ~ z_seg_g3 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + stu_res_official + fac_res_official + diverse_dorms + mentoring_programs + integration_courses + diversity_office + (1 |
                                                                                                                                                                                                                                                                     department_id),
    data = df %>% filter(reservation == 0)
  )

knitreg(
  list(lm3.1, lm3.2, lm3.3, lm3.4),
  custom.note = "%stars",
  stars = c(0.01, 0.05, 0.1),
  include.ci = FALSE,
  include.variance = TRUE,
  custom.model.names = c(
    "Cohort 1 Res",
    "Cohort 1 Non-res",
    "Cohort 2 Res",
    "Cohort 2 Non-res"
  ),
  omit.coef = "(female)|(b_score)|(ther_ed)|(area)|(^ses)|(hstype)|(age)|(official)|(school)|(seg)"
)
```


### Model ICC

```{r}
bind_rows(
  icc(lm3.1, by_group = T),
  icc(lm3.2, by_group = T),
  icc(lm3.3, by_group = T),
  icc(lm3.4, by_group = T),
  .id = "model"
) %>%
  pivot_wider(names_from = model, values_from = ICC) %>%
  select(
    level = Group,
    "Cohort 1 Res" = "1",
    "Cohort 1 Non-res" = "2",
    "Cohort 2 Res" = "3",
    "Cohort 2 Non-res" =  "4"
  ) %>%
  kable()
```


## Adding random slope

### Diverse Dorms

```{r, results="asis"}
lm4.1a <-
  lmer(
    z_seg_g2 ~ z_seg_g1 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + stu_res_official + fac_res_official + diverse_dorms + (1 + diverse_dorms |
                                                                                                                                                                                                       department_id),
    data = df %>% filter(reservation == 1)
  )

lm4.2a <-
  lmer(
    z_seg_g2 ~ z_seg_g1 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + stu_res_official + fac_res_official + diverse_dorms + (1 + diverse_dorms |
                                                                                                                                                                                                       department_id),
    data = df %>% filter(reservation == 0)
  )

lm4.3a <-
  lmer(
    z_seg_g4 ~ z_seg_g3 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + stu_res_official + fac_res_official + diverse_dorms + (1 + diverse_dorms |
                                                                                                                                                                                                       department_id),
    data = df %>% filter(reservation == 1)
  )

lm4.4a <-
  lmer(
    z_seg_g4 ~ z_seg_g3 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + stu_res_official + fac_res_official + diverse_dorms + (1 + diverse_dorms |
                                                                                                                                                                                                       department_id),
    data = df %>% filter(reservation == 0)
  )

knitreg(
  list(lm4.1a, lm4.2a, lm4.3a, lm4.4a),
  custom.note = "%stars",
  stars = c(0.01, 0.05, 0.1),
  include.ci = FALSE,
  include.variance = TRUE,
  custom.model.names = c(
    "Cohort 1 Res",
    "Cohort 1 Non-res",
    "Cohort 2 Res",
    "Cohort 2 Non-res"
  ),
  omit.coef = "(female)|(b_score)|(ther_ed)|(area)|(^ses)|(hstype)|(age)|(official)|(school)|(seg)"
)
```


### Mentoring Programs

```{r, results="asis"}
lm4.1b <-
  lmer(
    z_seg_g2 ~ z_seg_g1 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + stu_res_official + fac_res_official + mentoring_programs + (1 + mentoring_programs |
                                                                                                                                                                                                            department_id),
    data = df %>% filter(reservation == 1)
  )

lm4.2b <-
  lmer(
    z_seg_g2 ~ z_seg_g1 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + stu_res_official + fac_res_official + mentoring_programs + (1 + mentoring_programs |
                                                                                                                                                                                                            department_id),
    data = df %>% filter(reservation == 0)
  )

lm4.3b <-
  lmer(
    z_seg_g4 ~ z_seg_g3 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + stu_res_official + fac_res_official + mentoring_programs + (1 + mentoring_programs |
                                                                                                                                                                                                            department_id),
    data = df %>% filter(reservation == 1)
  )

lm4.4b <-
  lmer(
    z_seg_g4 ~ z_seg_g3 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + stu_res_official + fac_res_official + mentoring_programs + (1 + mentoring_programs |
                                                                                                                                                                                                            department_id),
    data = df %>% filter(reservation == 0)
  )

knitreg(
  list(lm4.1b, lm4.2b, lm4.3b, lm4.4b),
  custom.note = "%stars",
  stars = c(0.01, 0.05, 0.1),
  include.ci = FALSE,
  include.variance = TRUE,
  custom.model.names = c(
    "Cohort 1 Res",
    "Cohort 1 Non-res",
    "Cohort 2 Res",
    "Cohort 2 Non-res"
  ),
  omit.coef = "(female)|(b_score)|(ther_ed)|(area)|(^ses)|(hstype)|(age)|(official)|(school)|(seg)"
)
```


### Integration courses

```{r, results="asis"}
lm4.1c <-
  lmer(
    z_seg_g2 ~ z_seg_g1 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + stu_res_official + fac_res_official + integration_courses + (1 + integration_courses |
                                                                                                                                                                                                             department_id),
    data = df %>% filter(reservation == 1)
  )

lm4.2c <-
  lmer(
    z_seg_g2 ~ z_seg_g1 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + stu_res_official + fac_res_official + integration_courses + (1 + integration_courses |
                                                                                                                                                                                                             department_id),
    data = df %>% filter(reservation == 0)
  )

lm4.3c <-
  lmer(
    z_seg_g4 ~ z_seg_g3 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + stu_res_official + fac_res_official + integration_courses + (1 + integration_courses |
                                                                                                                                                                                                             department_id),
    data = df %>% filter(reservation == 1)
  )

lm4.4c <-
  lmer(
    z_seg_g4 ~ z_seg_g3 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + stu_res_official + fac_res_official + integration_courses + (1 + integration_courses |
                                                                                                                                                                                                             department_id),
    data = df %>% filter(reservation == 0)
  )

knitreg(
  list(lm4.1c, lm4.2c, lm4.3c, lm4.4c),
  custom.note = "%stars",
  stars = c(0.01, 0.05, 0.1),
  include.ci = FALSE,
  include.variance = TRUE,
  custom.model.names = c(
    "Cohort 1 Res",
    "Cohort 1 Non-res",
    "Cohort 2 Res",
    "Cohort 2 Non-res"
  ),
  omit.coef = "(female)|(b_score)|(ther_ed)|(area)|(^ses)|(hstype)|(age)|(official)|(school)|(seg)"
)
```


### Divresity Offices

```{r, results="asis"}
lm4.1d <-
  lmer(
    z_seg_g2 ~ z_seg_g1 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + stu_res_official + fac_res_official + diversity_office + (1 + diversity_office |
                                                                                                                                                                                                          department_id),
    data = df %>% filter(reservation == 1)
  )

lm4.2d <-
  lmer(
    z_seg_g2 ~ z_seg_g1 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + stu_res_official + fac_res_official + diversity_office + (1 + diversity_office |
                                                                                                                                                                                                          department_id),
    data = df %>% filter(reservation == 0)
  )

lm4.3d <-
  lmer(
    z_seg_g4 ~ z_seg_g3 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + stu_res_official + fac_res_official + diversity_office + (1 + diversity_office |
                                                                                                                                                                                                          department_id),
    data = df %>% filter(reservation == 1)
  )

lm4.4d <-
  lmer(
    z_seg_g4 ~ z_seg_g3 + female + age + ses + b_score + mother_ed_ind + father_ed_ind + b_i_area + b_eb1_hstype + b_i_school_years_english + stu_res_official + fac_res_official + diversity_office + (1 + diversity_office |
                                                                                                                                                                                                          department_id),
    data = df %>% filter(reservation == 0)
  )

knitreg(
  list(lm4.1d, lm4.2d, lm4.3d, lm4.4d),
  custom.note = "%stars",
  stars = c(0.01, 0.05, 0.1),
  include.ci = FALSE,
  include.variance = TRUE,
  custom.model.names = c(
    "Cohort 1 Res",
    "Cohort 1 Non-res",
    "Cohort 2 Res",
    "Cohort 2 Non-res"
  ),
  omit.coef = "(female)|(b_score)|(ther_ed)|(area)|(^ses)|(hstype)|(age)|(official)|(school)|(seg)"
)
```



## Model comparison

### Cohort 1 reservation

```{r}
compare_performance(lm1.1, lm2.1, lm3.1, lm4.1a, lm4.1b, lm4.1c, lm4.1d)
```

### Cohort 1 non-reservation

```{r}
compare_performance(lm1.2, lm2.2, lm3.2, lm4.2a, lm4.2b, lm4.2c, lm4.2d)
```

### Cohort 2 reservation

```{r}
compare_performance(lm1.3, lm2.3, lm3.3, lm4.3a, lm4.3b, lm4.3c, lm4.3d)
```

### Cohort 2 non-reservation

```{r}
compare_performance(lm1.4, lm2.4, lm3.4, lm4.4a, lm4.4b, lm4.4c, lm4.4d)
```



