---
title: "Segregation and Affirmative Action in College"
#subtitle: "⚔<br/>with xaringan"
author: "Saurabh Khanna"
#institute: "Stanford University"
#date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false

---

class: middle

# Research Questions

1. How do institutional policies affect segregation based on affirmative action quotas?

2. Do these impacts differ for advantaged versus disadvantaged students?

3. Do these impacts differ at elite versus non-elite institutions?


---

class: inverse, center, middle

# Data

---

class: middle

# Data

* 50 randomly sampled colleges
 + 200 classrooms (4 per college)
      - ~20000 students (averaging 100 per classroom)


* Network data for each classroom
  + Students nominate upto 10 friends
  + Longitudinal data - 2 time points

        
* Affirmative Action Policy
  + Quotas _reserved_ for students from historically disadvantaged backgrounds
  + __Reservation students__: Those who gain admission based on this quota
  + __Non-Reservation students__: Those who don't


---

class: inverse, center, middle

# Method 1
### Regression on Segregation Scores

---

class: middle

# Segregation Score

```{r table1, echo=FALSE, message=FALSE, warnings=FALSE}
library(tidyverse)
tribble(
    ~"", ~"Friend (f)", ~"Not friend (f')",   
    "Reservation (r)",    "A",     "C",
    "Non-reservation (nr)",    "B",     "D"
) %>%
knitr::kable(format = "html")
```
<br/>

Natural log of the odds that a student will nominate a friend in their own category, relative to the odds that they will nominate someone of a different category

$$segregation_{r} = log \left[\frac{f_{r}}{f_{nr}}\times\frac{f'_{nr}}{f'_{r}} \right] = log \left(\frac{AD}{BC} \right)$$
$$segregation_{nr} = log \left[\frac{f_{nr}}{f_{r}}\times\frac{f'_{r}}{f'_{nr}} \right] = log \left(\frac{BC}{AD} \right)$$

<br/>
$+$ score $\to$ More within category friendships <br/>
$-$ score $\to$ More across category friendships <br/>
0 $\to$ Optimum within/across category friendships (Preference = Opportunity)

---

# Model

For a reservation/non-reservation student $i$ at time points $t_1$ and $t_2$:
<br/><br/>

$$seg_{i,t_2} = \color{red}{policy_i} + \color{blue}{seg_{i,t_1} + gender_i + SES_i + rural_i + gpa_i + parented_i} + \epsilon_i$$

<br/><br/>
$\color{red}{policy_i}$ can be<sup>1</sup>:
1. Proportion of seats taken by _students_ from disadvantaged backgrounds
2. Proportion of seats taken by _faculty_ from disadvantaged backgrounds
3. Random assignment of students to dormitories
4. Random assignment of students to teaching sections
5. Student taught courses and seminars to encourage integration
6. Mentoring programs for students

.footnote_tiny[[1] 1-4 implicit, 5-6 explicit]

---

# Findings

* Non-reservation students more segregated at all colleges

* Overall segregation sustains sustains more over time at elite colleges

* _Implicit_ institutional policies significantly reduce segregation
  * Stronger effects at elite colleges

* _Explicit_ policies for reducing segregation have no effect 

---

class: inverse, center, middle

# Method 2
### STERGM

---

# Model - Level 1

For each of the 200 classrooms, I run:

```{r, eval = F}
stergm(
  list(network_t1, network_t2),
  formation = 
    ~ edges + nodefactor("reservation") + nodematch("reservation") + nodefactor("female") + nodematch("female") + nodefactor("ses") + nodematch("ses") + nodefactor("area") + nodematch("area") + nodecov("score") + absdiff("score") + mutual + gwesp(0.25),
  dissolution = 
    ~ edges + nodefactor("reservation") + nodematch("reservation") + nodefactor("female") + nodematch("female") + nodefactor("ses") + nodematch("ses") + nodefactor("area") + nodematch("area") + nodecov("score") + absdiff("score") + mutual + gwesp(0.25),
  estimate = "CMLE",
  times = 1:2,
  control = control.stergm(seed = 100, MLE.MCMC.burnin=50000, CMLE.MCMC.interval=2000)
)
```


<br/>
No convergence for 35 classrooms

Degenerate results for 43 classrooms

---

# Model - Level 2

Extracting model coefficients and standard errors

Synthesizing effect sizes using a Random effects model

Meta-regression using level 2 covariates like<sup>1</sup>:
1. Proportion of seats taken by _students_ from disadvantaged backgrounds
2. Proportion of seats taken by _faculty_ from disadvantaged backgrounds
3. Random assignment of students to dormitories
4. Random assignment of students to teaching sections
5. Student taught courses and seminars to encourage integration
6. Mentoring programs for students

.footnote_tiny[[1] 1-4 implicit, 5-6 explicit]

---

# Findings

### Level 1
* Homophilous connections based on affirmative action status 48% likely to form and persist
* Homophilous connections based on gender 43% likely to form and 45% likely to persist
* Reciprocal relations 78% likely to form and 83% likely to persist
* Clustered relations 63% likely to form and 65% likely to persist

### Level 2
* Signs match regression model results (implicit policies reducing affirmative action based homophily), but not significant


---

# Missing Network Data


Absenteeism and non-response across 2 time points

<br/>
Existing approaches
* Simple imputation (biased for sparse networks)
* Multiple imputation based on ERGM/SAOM (prediction $\approx$ imputation)

<br/>
Testing another approach
* Collaborative filtering approaches on network adjacency matrix

---

class: middle

Thank You!

<br/><br/><br/>

Code here: https://github.com/saurabh-khanna

Help with `imputenet`:
```{r, eval=FALSE, message=FALSE, warnings=FALSE}
devtools::install_github("saurabh-khanna/imputenet")
```








