---
title: "Segregation and Affirmative Action in college"
#subtitle: "⚔<br/>with xaringan"
author: "Saurabh Khanna"
#institute: "Stanford University"
#date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false

---

class: inverse, center, middle

# Data and Methods

---

class: middle

# Data

* 50 randomly sampled colleges
 + 200 classrooms (4 per college)
      - ~20000 students (averaging 100 per classroom)


* Network data for each classroom
  + Students nominate upto 10 friends
  + Panel data for 2 cohorts
        - $t_1$: Surveyed students in year 1 and year 3 of college
        - $t_2$: Surveyed _same students_ (now in year 2 and year 4 of college)

        
* Affirmative Action Policy
  + Seats reserved for students historically disadvantaged backgrounds
  + _Reservation students_: Those who gain admission based on this policy
  + _Non-Reservation students_: Those who don't


---

class: middle

# Segregation Score

```{r table, echo=FALSE, message=FALSE, warnings=FALSE}
library(tidyverse)
tribble(
    ~"", ~"Friend (f)", ~"Not friend (f')",   
    "Reservation (r)",    "4",     "36",
    "Non-reservation (nr)",    "6",     "54"
) %>%
knitr::kable(format = "html")
```
<br/>

Natural log of the odds that a student will nominate a friend in their own category, relative to the odds that they will nominate someone of a different category

$$segregation_{r} = log \left[\frac{f_{r}}{f_{nr}}\times\frac{f'_{nr}}{f'_{r}} \right]$$
$$segregation_{nr} = log \left[\frac{f_{nr}}{f_{r}}\times\frac{f'_{r}}{f'_{nr}} \right]$$

<br/>
$+$ score $\to$ More same category friendships <br/>
$-$ score $\to$ More different category friendships <br/>
0 $\to$ Optimum same/different category friendships (Preference = Opportunity)

---

# Model

For student $i$ at time points $t_1$ and $t_2$:
<br/><br/>

$$seg_{i,t_2} = \color{red}{policy_i} + \color{blue}{seg_{i,t_1} + gender_i + SES_i + rural_i + age_i} + \epsilon_i$$

<br/><br/>
$\color{red}{policy_i}$ can be<sup>1</sup>:
1. Proportion of seats reserved for _students_ from disadvantaged backgrounds
2. Proportion of seats reserved for _faculty_ from disadvantaged backgrounds
3. Students from different backgrounds being placed together in _same dormitories_ by design
4. Students from different backgrounds being placed together in _same teaching sections_ by design
5. Student taught courses and seminars to encourage integration
6. Mentoring programs for students

.footnote_tiny[[1] 1-2 continuous, 3-6 categorical]

---

# STERGM

For each of the 200 classrooms, I run:

```{r, eval = F}
stergm(
  list(network_t1, network_t2),
  formation = 
    ~ edges + nodefactor("reservation") + nodematch("reservation", diff = TRUE) + mutual + cyclicalties  + transitiveties,
  dissolution = 
    ~ edges + nodefactor("reservation") + nodematch("reservation", diff = TRUE) + mutual + cyclicalties  + transitiveties,
  estimate = "CMLE",
  times = 1:2,
  control = control.stergm(seed = 100, MLE.MCMC.burnin=50000, CMLE.MCMC.interval=2000)
)
```


* Model does not converge for 6 classrooms
* Degenerate results for 88 classrooms

---

# Meta-analysis

Extracting model coefficients and standard errors

Synthesizing effect sizes using a Random effects model

* Reciprocal and Transitive ties are significant in tie formation and tie persistence
* Cyclical ties have significantly lower changes of formation
* Reservation students are less likely to form new ties (unstable)

<br/><br/>
#### Next: 
Meta-regression using level 2 covariates (like classroom/departmental policies)











